LEMONADE: Leveraging Modern Automated Deduction for Program Synthesis\\ \vspace{0.5cm} \large{WWTF ICT 2022}

### 2022-04-03 WWTF/main.tex
asdf

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
However, since non-constructive tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ are classically provable, we lose the realizability of $\exists$ and $\vee$.
As discussed in~\cite{practical}, in practice it is sometimes possible to eliminate the non-constructive reasoning steps from proofs.
We aim to establish stronger theoretical guarantees on when this is possible but also evaluate this approach when realizability is not ensured by a theorem.

>>>>

1) Parigot's $\lambda\mu$-calculus~\cite{Parigot1} gives a direct translation of classical proofs with datatypes and is essentially ready for implementation.
Unfortunately, we loose the realizability of $\exists$ and $\vee$, since non-constructive tautologies like $\neg\forall xA(x)\to \exists x\neg A(x)$ or $A\vee \neg A$ are classically provable.
As discussed in~\cite{practical}, in practice it is sometimes possible to eliminate the non-constructive reasoning steps from proofs.
We aim to establish stronger theoretical guarantees on when this is possible but also evaluate this approach when realizability is not ensured by a theorem.
